### 2016-12-12 R/ITHIM.Rmd
Created more figures for WI/MI/OH

foo <- subset(foo, state %in% c("WI", "MI","OH"))

@@

p <- ggplot(D, aes(state, value/1e3, fill = variable))
p + geom_bar(stat= "identity") + scale_x_discrete(name="") + scale_y_continuous(name="Thousands of DALYs") + guides(fill=FALSE) + scale_fill_manual(values=cbPalette) + coord_cartesian(ylim = c(175, 600)) + theme(axis.text.y  = element_text(size = 16)) + theme(axis.text.x  = element_text(size = 16), axis.title.x  = element_text(size = 16)) + coord_flip()

>>>>

foo <- subset(foo, state %in% c("MI","OH"))

@@

p <- ggplot(D, aes(state, value/1e3, fill = variable))
p + geom_bar(stat= "identity") + scale_x_discrete(name="") + scale_y_continuous(name="Thousands of DALYs") + guides(fill=FALSE) + scale_fill_manual(values=cbPalette) + theme(axis.text.y  = element_text(size = 16)) + theme(axis.text.x  = element_text(size = 16), axis.title.x  = element_text(size = 16)) + coord_flip() # + coord_cartesian(ylim = c(175, 600))
```

```{r rustBelt2, eval = TRUE, dev=c('pdf', 'png'), fig.width = 2*fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}

D <- rbind(data.frame(getWalkTime(ITHIMList[["MI"]]),state = "MI"), data.frame(getWalkTime(ITHIMList[["WI"]]),state = "WI"), data.frame(getWalkTime(ITHIMList[["OH"]]),state = "OH"))

p <- ggplot(subset(D, ageClass != "ageClass1"), aes(x = ageClass, y = mu, fill = state)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + facet_grid( . ~ sex) + scale_x_discrete(name="", labels = c("5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="Time Walking per Week (minutes)") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8)) + scale_fill_manual(values=cbPalette[-3])
```
